---
title: "Homework 04 - Data Classes w. forcats & lubridate"
author: "Damian Velasco"
date: "3/9/23"
output: html_document
---

### Load packages and data

```{r load-packages, message=FALSE}
library(tidyverse)
library(openintro) 
library(lubridate)
```

## Exercises

### Exercise 1

```{r}
c("5", "length = 5", "5L")
```
`r typeof("5")`

### Exercise 2

```{r bind_data , eval = F}
data_frame() <- bind_cols("numeric" = numeric, "___" = character, "___" = ___)
___
```
### Exercise 3

Remove this text, and add your answer for Exercise 3 here.

### Exercise 4

Remove this text, and add your answer for Exercise 4 here.

### Exercise 5

Remove this text, and add your answer for Exercise 5 here.

### Exercise 6

Remove this text, and add your answer for Exercise 6 here.

### Exercise 7

Remove this text, and add your answer for Exercise 7 here.

### Exercise 8

Remove this text, and add your answer for Exercise 8 here.

### Exercise 9

Remove this text, and add your answer for Exercise 9 here.

### Exercise 10

Remove this text, and add your answer for Exercise 10 here.
