---
title: "Homework 04 - Data Classes w. forcats & lubridate"
author: "Damian Velasco"
date: "3/9/23"
output: html_document
---

### Load packages and data

```{r load-packages, message=FALSE}
library(tidyverse)
library(openintro) 
library(lubridate)
library(glue)
```

## Exercises

### Exercise 1

```{r eval=TRUE}

numeric <- c(1,2,3,4,5)
character <- c("A","B","C","D","E")
mixed <- c("A", 2, "C", 4, "E")

 typeof(c(1,2,3,4,5))
 typeof(c("A","B","C","D","E"))
 typeof(c("A", 2, "C", 4, "E"))
class(character)
class(numeric)
class(mixed)
```
### Exercise 2

```{r bind_data , eval = TRUE}
data_frame <- bind_cols("numeric" = numeric, "character" = character, "mixed" = mixed)
typeof(data_frame)
```
### Exercise 3

```{r eval= FALSE}
numeric <- c(1,2,3,4,5)
character <- c("A","B","C","D","E")
mixed <- c("A", 2, "C", 4)
bind_cols("numeric" = numeric, "character" = character, "mixed" = mixed)
```
In this, the error would be that there is a size of 4 and not of 5. And because of this the data chuck will not load. 

### Exercise 4

```{r , eval = TRUE}
my_list <- list("numeric" = numeric, "character" = character, "mixed" = mixed)
my_list
```
This data is marked to be as completed and the other data was not complete. 
### Exercise 5

```{r earthquakes-factors}
earthquakes %>% 
  ggplot(aes(x = month)) +
  geom_bar() +
  labs(x = "Month of the year", y = "Earthquake count")
```
The data type for this coercion is going in a formal matter and not the normal way. This data is weird because it is in alphabetical order and not in the normal order the months go. 

### Exercise 6

```{r earthquakes-forcats-1}
earthquakes %>% 
  ggplot(aes(x = fct_infreq(month))) +
  geom_bar() +
  labs(x = "Month of the year", y = "Earthquake count")
```
This one is going from most to least.
```{r earthquakes-forcats-2}
earthquakes %>% 
  ggplot(aes(x = fct_rev(month))) +
  geom_bar() +
  labs(x = "Month of the year", y = "Earthquake count")
```
This data type is going in backward order.
```{r earthquakes-forcats-3}
earthquakes %>% 
  ggplot(aes(x = fct_inorder(month))) +
  geom_bar() +
  labs(x = "Month of the year", y = "Earthquake count")
```
This one is about when it comes up in first appearance. 
```{r earthquakes-forcats-4}
earthquakes %>% 
  ggplot(aes(x = month %>% fct_infreq() %>% fct_rev())) +
  geom_bar() +
  labs(x = "Month of the year", y = "Earthquake count")
```
this one is going in increasing order.
```{r earthquakes-forcats-5}
earthquakes %>% 
  mutate(month = fct_recode(month,
                            "1" = "January",
                            "2" = "February",
                            "3" = "March",
                            "4" = "April",
                            "5" = "May",
                            "6" = "June",
                            "7" = "July",
                            "8" = "August",
                            "9" = "September",
                            "10" = "October",
                            "11" = "November",
                            "12" = "December")) %>% 
  ggplot(aes(x = factor(as.numeric(month)))) +
  geom_bar() +
  labs(x = "Month of the year", y = "Earthquake count")
```
This one is going in numerical order 

### Exercise 7
In this data, the second and third are being separated by the month and the year.
`r typeof(year)`
`r typeof(month)`
The date would be combining the year month and day together into one vector. 
```{r earthquake-dates}
earthquakes_new <- earthquakes %>% 
  mutate(date = glue("{year} {month} {day}")) %>% 
  relocate(date)
print(earthquakes_new)
```


### Exercise 8

```{r earthquakes-dates}
 earthquakes_new %>%
  mutate(date = glue("{year} {month} {day}")) %>% 
  relocate(date) %>%
  filter(year == "1933") %>%
  ggplot( aes(x = date, y = richter))+
  geom_point()
```  

In this plot the months are not in the correct order. 

### Exercise 9
```{r earthquakes-dates2, eval = F}
earthquakes %>% 
  mutate(date = ymd(glue("{year} {month} {day}"))) %>% 
  relocate(date) %>% 
  ggplot(aes(x = date, y = richter)) +
  geom_point() 
```


