---
title: "Lab 04 - Data Type Coercion"
author: "Damian Velasco"
date: "3/7/2023"
output: html_document
---

### Load packages and data

```{r load-packages, message = FALSE}
library(tidyverse)
library(openintro)
```

## Exercises

### Exercise 1

```{r echo = F}
1
1L
"C"
```
1 is type double 
1L is type integer
C is type character 

1 is type `r typeof(1)`

```{r echo = F}
c(1, 1L, "C")
```

The second code chunk creates a vector thats more organized and the second one makes them the characters 

```{r echo = F}
typeof(c(1, 1L, "C"))
```
the third code chunk makes it type`r typeof(c(1,1L,"c"))`

### Exercise 2

```{r echo = F}
1:3
5
```
1:3 is `r typeof(1:3)`
5 is `r typeof(5)`

```{r echo = F}
typeof(c(1:3, 5))
```
this is a type`r typeof(c(1:3, 5))`



### Exercise 3

Remove this text, and add your answer for Exercise 3 here.

### Exercise 4

Remove this text, and add your answer for Exercise 4 here.

### Exercise 5

Remove this text, and add your answer for Exercise 5 here.

### Exercise 6

Remove this text, and add your answer for Exercise 6 here.

### Exercise 7

Remove this text, and add your answer for Exercise 7 here.

### Exercise 8

Remove this text, and add your answer for Exercise 8 here.

### Exercise 9

Remove this text, and add your answer for Exercise 9 here.

### Exercise 10

Remove this text, and add your answer for Exercise 9 here.
