---
title: "Lab 04 - Data Type Coercion"
author: "Damian Velasco"
date: "3/7/2023"
output: html_document
---

### Load packages and data

```{r load-packages, message = FALSE}
library(tidyverse)
library(openintro)
```

## Exercises

### Exercise 1

```{r echo = F}
1
1L
"C"
```
1 is type double 
1L is type integer
C is type character 

1 is type `r typeof(1)`

```{r echo = F}
c(1, 1L, "C")
```

The second code chunk creates a vector thats more organized and the second one makes them the characters 

```{r echo = F}
typeof(c(1, 1L, "C"))
```
the third code chunk makes it type`r typeof(c(1,1L,"c"))` because the characters overtake the integers

### Exercise 2

```{r echo = F}
1:3
5
```
1:3 is `r typeof(1:3)`
5 is `r typeof(5)`

```{r echo = F}
typeof(c(1:3, 5))
```
this is a type`r typeof(c(1:3, 5))`

These would be because 5 is a integer 

### Exercise 3

```{r echo = F}
3 
FALSE
T
```
3 is a type `r typeof(3)`
false is type `r typeof(FALSE)`
T is type `r typeof(T)`
```{r echo = F}
typeof(c(3, FALSE, T))
```
the vector type for this is `r typeof(c(3, FALSE, T))`
doubles takeover logical
### Exercise 4

```{r echo = F}
TRUE
as.numeric(TRUE)
```
TRUE is type `r typeof(TRUE)`
As TRUE is take double, 

```{r echo = F}
typeof(c(TRUE, as.numeric(TRUE)))
```
this vector is type is a double, and a double overtakes logical

### Exercise 5
```{r echo = F}
NA
FALSE
as.logical(1)
```
NA is type  `r typeof(NA)`
`r typeof(FALSE)`
`r typeof(as.logical(1))`
```{r echo = F}
typeof(c(NA, FALSE, as.logical(1)))
```
Every object is logical in this vector

### Exercise 6

```{r echo = F}
1L
0
1L / 0
"A"
```
1L is a type `r typeof(1L)`
0 is a type `r typeof(0)`
1L / 0 is a type `r typeof(1L / 0)`

```{r echo = F}
typeof(c(1L / 0, "A"))
```
this cold chunk is a `r typeof( c(1L /0, "A"))` and this is because the character overtakes the doubles

### Exercise 7

``` {r}
glimpse(earthquakes)
```

### Exercise 8

the two data types would be year and richer

### Exercise 9
This would see them as individuals and because there are many repeated years, the data would be extended out more than it needs to be.

### Exercise 10

```{r major, eval = T}
earthquakes %>% 
  mutate(major = case_when(
    richter > 7.5 ~ TRUE,
    TRUE ~ FALSE
  )) %>% 
  mutate(major = as.numeric(major)) %>% 
  filter(major == TRUE)
```
